An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
walk through Algorithm 1

We would like a BFS on evolving graphs to work similar to that on graphs: the search starts with some source node $(s,t)$, called \emph{root}. It constructs a tree through discovering all nodes that are reachable by
temporal paths of length $k$ before moving to all nodes that are reachable by
 temporal paths of length $k+1$.
By construction, the time stamp of an active node is always not later than
that of its descendant. Suppose we
start with node $(1, t_1)$ in Figure \ref{fig:eg_shortest_path}.
After $1$ temporal path from $(1, t_1)$, we can reach
$(2, t_1)$ and $(1, t_2)$. After $2$ temporal paths, we can reach
$(2, t_1), (1, t_2), (2, t_2)$ and $(3, t_2)$.
% This example motivates us to define the reachable set of
% a node-timestamp pair.
Formally, we define the \emph{forward-neighbors} of a node $(v, t)$ to
be the set of all the reachable nodes after $1$ temporal path from
$(v, t)$, i.e., the nodes pointed by $v$ at time stamp $t$ and
the active node $v$ itself at later time stamps. In Figure
\ref{fig:eg_shortest_path},
the forward-neighbors of $(1, t_1)$  are $(2, t_1)$ and $(1, t_2)$ and
the forward-neighbors of $(2, t_1)$ is $(2, t_3)$.
See Algorithm  \ref{alg:bfs} for the evolving-graph BFS algorithm.

>>>>

We would like a BFS on evolving graphs to work similar to that on graphs: the search starts with some source node $(s,t)$, called \emph{root}. It constructs a tree through discovering all nodes that are reachable by
temporal paths of length $k$ before moving to all nodes that are reachable by
 temporal paths of length $k+1$.
By construction, the time stamp of an active node is always not later than
that of its descendant. Suppose we
start with node $(1, t_1)$ in Figure \ref{fig:eg_shortest_path}.
After $1$ temporal path from $(1, t_1)$, we can reach
$(2, t_1)$ and $(1, t_2)$. After $2$ temporal paths, we can reach
$(2, t_1), (1, t_2), (2, t_2)$ and $(3, t_2)$.
% This example motivates us to define the reachable set of
% a node-timestamp pair.
Formally, we define the \emph{forward-neighbors} of a node $(v, t)$ to
be the set of all the reachable nodes after $1$ temporal path from
$(v, t)$, i.e., the nodes pointed by $v$ at time stamp $t$ and
the active node $v$ itself at later time stamps. In Figure
\ref{fig:eg_shortest_path},
the forward-neighbors of $(1, t_1)$  are $(2, t_1)$ and $(1, t_2)$ and
the forward-neighbors of $(2, t_1)$ is $(2, t_3)$.

Given an evolving graph $G_n$ and a starting active node $(s,t)$, Algorithm \ref{alg:bfs} 
returns all the reachable active nodes and their distances from $(s,t)$. 
For Figure \ref{fig:eg_shortest_path}, suppose we start with $(1, t_2)$, then
$frontier$ is $\langle(1,t_2)\rangle$ after step $5$.  Since the only forward-neighbor of 
$(1,t_2)$ is $(3,t_2)$, $dict.(3,t_2) =1$ at step $11$ and $next$ is enqueued to be 
$\langle (3,t_2) \rangle$ at step $12$. After that $frontier$ is equal to $next$. Since 
$frontier$ is not empty, we go through step $7$-$12$ again. This time 
the forward-neighbor of $(3,t_2)$ is $(3,t_3)$, so $dict.(3,t_3)=2$ and 
$next = \langle (3,t_3) \rangle$ and so on. The loop terminates when $frontier$ is empty.
